Tactic Script Optimisation for Aesop

### 2024-09-10 paper.tex
Reformat "i^th"

The index of each inner node is the position of the node's step in the original sequence, i.e.\ 1 for $s₁$ etc.
From this immediately follows that the children of a node with index $i$ must each have an index greater than $i$ since a step that applies to the post-goal of the $i$th step cannot have been run before the $i$th step.

>>>>

The index of each inner node is the position of the node's step in the original sequence, i.e.\ 1 for $s₁$ etc.
From this immediately follows that the children of a node with index $i$ must each have an index greater than $i$ since a step that applies to the post-goal of the $i^{\text{th}}$ step cannot have been run before the $i^{\text{th}}$ step.
